---
title: "INFORMATIVE PLOT TITLE"
subtitle: "From [UCSB Young Lab R Graph Gallery](https://github.com/ucsbyounglab/figure-inspiration)"
author: "YOUR NAME, YOUR EMAIL"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  html_document:
    theme: flatly
    highlight: tango
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = '..')
knitr::opts_chunk$set(fig.align='center', collapse=TRUE, warning=FALSE, message=FALSE)
```

---

### Figure information

- Figure caption/description
- Suggested analyses
- Citation/link if published
- Links to relevant resources
- Any other useful notes

---

### Figure code
<br>

#### **Packages**

- List necessary packages

```{r packages}

### Load packages
library(tidyverse) # needed for ggsave function

```

#### **Data**

- Brief description of the data
- Relevant columns
  - `COLUMN_NAME`: definition
  - `COLUMN_NAME`: definition
  - `COLUMN_NAME`: definition

```{r data}

### Load data

### Data structure
str()
head()

```

#### **Data wrangling**

- Describe necessary data wrangling (e.g. reordering variables, creating matrices)

```{r data-wrangling}

### Data wrangling

```

#### **Figure**

```{r figure, fig.width=5, fig.height=3, class.source = 'fold-show'}

### Adjust fig.width and fig.height in the code chunk options to optimize figure sizing

### Create figure
fig_1 <- 

```

```{r figure-save, include=FALSE}

### Save plot in "figures" folder
### Replace FILENAME with the name of the Rmd copied exactly (e.g. "facetted_boxplots")
### If only creating one figure, leave "_1" appended
### If creating multiple figures, copy the ggsave code for each figure and update with "_2", etc.
### Update the plotname, width, and height if needed
ggsave('figures/FILENAME_1.png', plot = fig_1,
       width = 5, height = 3, units = 'in')

```

---

### R session info

```{r sessionInfo}
sessionInfo()
```

<br>