---
title: "Habitat preference (Proportional abundance by habitat type)"
subtitle: "From [UCSB Young Lab R Graph Gallery](https://github.com/ucsbyounglab/figure-inspiration)"
author: "Kate Culhane, kathrynculhane@ucsb.edu"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  html_document:
    theme: flatly
    highlight: tango
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = '..')
knitr::opts_chunk$set(fig.align='center', collapse=TRUE)
```

---

### Figure information

- Caption: Small mammal habitat preference across fire severity categories. Bar plot showing the percentage of unique individuals trapped in each of the three fire severity categories for each of the 11 species captured, with number of total captures denoted by n. 
- Pairs well with NMDS ordination
- Published in Culhane et al. 2021 (in prep)
- Inspired by [Young et al. 2015](https://esajournals.onlinelibrary.wiley.com/doi/full/10.1890/14-0995.1) - Fig. 2b

---

### Figure code
<br>

#### **Packages**

- `tidyverse`

```{r}

# Load packages
library(tidyverse)

```

#### **Data**

- Small mammal capture data (one row per unique individual)
- Relevant columns
  - `severity`: treatment(fire severity: unburned, low/moderate, high)
  - `species`: small mammal species code
  - `common_name`: small mammal species common name

```{r}

# Load data
smamms <- read_csv('community_analysis/habitat_preference_data.csv') %>% 
  mutate(severity = factor(severity, levels = c('unb', 'mod', 'high')))

# Data structure
str(smamms)
head(smamms)

```

#### **Data wrangling**

- Create summary data table for samples size (n)
- Calculate proportional abundance per treatment, for each species
- Reorder factor levels by proportion

```{r}

# Summary table of overall mammal abundances
summary <- smamms %>% 
  group_by(species) %>% 
  summarize(n = length(species)) %>% 
  ungroup() %>% 
  arrange(-n)

# Dataframe of proportional abundance per fire severity, for each species
prop_species <- smamms %>% 
  group_by(species, common_name, severity) %>% 
  summarize(n = length(severity)) %>% 
  mutate(prop = n/sum(n)*100) %>% # proportion of captures at each treatment, per species
  mutate(label = common_name) %>% 
  ungroup()

# Dataframe for just low severity
prop_low <- prop_species %>% 
  filter(severity == 'unb') %>% 
  select(species, prop) %>% 
  rename(prop_low = prop)

# Dataframe for just moderate severity
prop_mod <- prop_species %>%
  filter(severity == 'mod') %>% 
  select(species, prop) %>% 
  rename(prop_mod = prop)

# Re-ordering data frame occurence within each severity
prop_species2 <- prop_species %>%
  full_join(prop_low, by = 'species') %>% 
  full_join(prop_mod, by = 'species') %>% 
  mutate(
    prop_low = case_when(
      is.na(prop_low) ~ 0,
      !is.na(prop_low) ~ prop_low
    ),
    prop_mod = case_when(
      is.na(prop_mod) ~ 0,
      !is.na(prop_mod) ~ prop_mod
    )
  ) %>% 
  ungroup() %>% 
  mutate(label = as_factor(label),
         label = fct_reorder(label, prop_mod),
         label = fct_reorder(label, prop_low),
         severity = factor(severity, levels = c('high', 'mod', 'unb'))) %>% 
  full_join(summary, by = 'species')

```

#### **Figure**

```{r, fig.width=4, fig.height=3}

# Column graph of proportional treatment abundances per species
colors <- c("#D85F2B", "#DCA827", "#2D9875")
ggplot(prop_species2, aes(x = label, y = prop, fill = severity)) +
  geom_col() +
  geom_text(aes(x = label, y = 103,
                label = paste('n = ', n.y)),
            size = 3.2, hjust = 0, color = 'grey30') +
  scale_fill_manual(values = colors,
                    name = 'Fire severity',
                    labels = labs) +
  coord_flip() +
  scale_y_continuous(limits = c(0, 200),
                     breaks = c(0, 50, 100),
                     expand = c(0,0)) +
  theme_minimal() +
  labs(x = '', y = '') +
  theme(axis.text.y = element_text(size = 10, color = 'black'),
        axis.text.x = element_text(size = 10),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        legend.position = 'none',
        axis.title.x = element_text(hjust = 3.8, size = 13))

```

```{r include=FALSE}
# Save plot
ggsave('figures/habitat_preference_1.png', plot = last_plot(),
       width = 4, height = 3, units = 'in')
```

---

### R session info

```{r sessionInfo}
sessionInfo()
```

<br>